Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-10 ltx/data_paper/DataPaper.tex
edits to results discussion and the conclusion

The third term in \eqref{eq:Voldermont} is obtained using the same method in \cite{Shumway2000}, i.e. by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1}^b \mathbf{\hat{x}}_{t+1}^{b\top} \mathbf C^\top$ to the expectation of the second term in \eqref{eq:Qfunctiontrace1} and then exploiting the expression given in \eqref{eq:EM-Xi0derivation1} . By defining $\Xi$-variables as 

@@

The covariance and cross-covariance terms in \eqref{eq:VoldermontwitXivariables}, consist of both the linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$. Finding the linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly from the smoother outputs, i.e. $\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ \cite{Gibsona2005}. To show how it can be done, the smoothed covariance matrix at time $t+1$ can be written as

@@

However calculation of the non-linear $\boldsymbol\Xi$-variables is not straightforward as in the linear case. Therefore, an additional Taylor expansion step to the URTSS algorithm is also created to linearise $\mathbf q(\mathbf{x}_t)$, enabling the  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$ using the smoother outputs. This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function at each time instant  around the smoothed state, $\hat{\mathbf x}_t^b$, i.e.

>>>>

The third term in \eqref{eq:Voldermont} is obtained using the same method in \cite{Shumway2000}, i.e. by adding and subtracting $\mathbf C \mathbf{\hat{x}}_{t+1}^b \mathbf{\hat{x}}_{t+1}^{b\top} \mathbf C^\top$ to the expectation of the second term in \eqref{eq:EM-Qfunctiontrace1} and then exploiting the expression given in \eqref{eq:EM-Xi0derivation1} . By defining $\boldsymbol\Xi$-variables as 

@@

The covariance and cross-covariance terms in \eqref{eq:VoldermontwitXivariables} consist of both the linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and the non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$. Finding the linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly from the smoother outputs, i.e. $\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ \cite{Gibsona2005}. To show how it can be done, the smoothed covariance matrix at time $t+1$ can be written as

@@

However, calculation of the non-linear $\boldsymbol\Xi$-variables is not straightforward as in the linear case. Therefore, an additional Taylor expansion step to the URTSS algorithm is also created to linearise $\mathbf q(\mathbf{x}_t)$, enabling the calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$ from the smoother outputs. This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function at each time instant  around the smoothed state, $\hat{\mathbf x}_t^b$, i.e.
